\thispagestyle{plain}
\addcontentsline{toc}{chapter}{General Introduction}
\section*{General Introduction}

Companies today must constantly evolve to remain competitive, especially in the digital
world where technological innovation accelerates at an unprecedented rate. In such an
environment, the ability to deliver reliable, high-quality software while meeting customer
expectations becomes a decisive factor for success. Ensuring customer satisfaction requires
not only building solid products but also guaranteeing their availability, performance,
and scalability. These concerns naturally push modern organizations toward cloud-native
architectures and DevOps practices that streamline delivery and improve operational
efficiency.

It is within this context that our internship project was conceived. The company
\textbf{The Mashroom} is currently developing a software solution whose infrastructure
is still based on an outdated setup relying on a single virtual machine. In this
configuration, the backend, frontend, and database all run on the same instance, which
results in performance degradation, service interruptions, and operational limitations as
the number of users increases. The growing demand on the platform has exposed clear
scalability limits, making the need for a modern, distributed, and cloud-ready infrastructure
a strategic priority.

The main objective of this project is therefore to migrate the existing system from its
monolithic, single-server environment to a scalable cloud architecture capable of adapting
to evolving workloads. This involves redesigning the deployment model, introducing
service separation, ensuring proper communication between components, and establishing
an automated workflow that improves reliability and accelerates delivery. In addition,
the new infrastructure must ensure high availability, better resource utilization, and a
more robust operational process that supports continuous updates without interrupting the
service.

This report is structured to guide the reader through the different phases of the project.
The first chapter introduces the general framework of the internship, outlines the company,
and presents the problem at hand. The following chapters will progressively define the
concepts related to modern cloud infrastructures, analyze the shortcomings of the old
system, and detail the proposed architecture for the new environment. Finally, the last
part of the report will focus on the implementation, describing the steps taken to rebuild
the infrastructure, automate the delivery pipeline, and ensure that the platform is fully
prepared for scalable and reliable operation.

\newpage